---
title: "Creating Shiny Apps for Stock Prediction"
author: "Hum N. Bhandari"
date: "11/21/2015"
output: html_document
---

###**Loading Data** 
We use Smarket data set from ISLR pacakge available in CRAN

```{r,cache=TRUE}
library(ISLR)
data(Smarket)
head(Smarket)
```

###**Creating Model**
Now,we use linear regression prediction model to predict the Today's precentage return from stocks 
Now lets fit linear regresion model to predict Today's stocks by using 5 days records 
Lag1, Lag2, Lag3, Lag4, and Lag5 

```{r,}
fit<-lm(Today~Lag1+Lag2+Lag3+Lag4+Lag5, data = Smarket)
summary(fit)
```

###**Predicting today's stock**

```{r,cache=TRUE}
predict(fit,newdata=data.frame(Lag1 = 0.1,Lag2 = 0.1,Lag3 = 0.1,Lag4 = 0.1, Lag5 = 0.1) )
```



##**Creating Shiny Apps**

**ui.R file**

```{r,eval=FALSE}

library(shiny)
library(ISLR)

shinyUI(
  
  pageWithSidebar(
    
    headerPanel("Predicting percentage returns from stocks"),
    
    sidebarPanel(
      
      numericInput('Lag1','Enter percentage returns 1 day before', 0.1 , min = -5, max = 5, step =.05),
      #submitButton('Submit'),
     
      numericInput('Lag2', 'Enter percentage returns 2 days before', 0.1 , min = -5, max = 5, step =.05),
     # submitButton('Submit'),
      numericInput('Lag3', 'Enter percentage returns 3 days before', 0.1 , min = -5, max = 5, step =.05),
     # submitButton('Submit'),
      numericInput('Lag4', 'Enter percentage returns 4 days before', 0.1 , min = -5, max = 5, step =.05),
     # submitButton('Submit'),
      numericInput('Lag5', 'Enter percentage returns 5 days before', 0.1 , min = -5, max = 5, step =.05),
      submitButton('Submit')
    ),
    
    mainPanel(
      h3('Results of the prediction'),
      p('This apps use  last five days percentage return records to predict today\'s stok returns
        using  linear regression model'),
     
      h4('Today\'s  percentage returns prediction from stocks is'),
      verbatimTextOutput("prediction"),
      
     h4('How to use this Apps??'),
     p('1.Enter values of last five day\'s return from stocks in five boxes'),
     p('2.Press the Submit button to get prediction'),
     p('3.Default value for each day\'s return is 0.1 '),
     p('4.You can increase or decrease the values for each last day by 0.05 between -5 to 5')
    )
  )
)

```

**server.R file**

```{r,eval=FALSE}
library(shiny)
library(ISLR)
data(Smarket)
suppressPackageStartupMessages(library(googleVis))
fit<-lm(Today~Lag1+Lag2+Lag3+Lag4+Lag5,data = Smarket)
shinyServer(
  function(input, output) {
    output$Lag1 <- renderPrint({input$Lag1})
    output$Lag2 <- renderPrint({input$Lag2})
    output$Lag3 <- renderPrint({input$Lag3})
    output$Lag4 <- renderPrint({input$Lag4})
    output$Lag5 <- renderPrint({input$Lag5})
    
    newdata <- reactive(data.frame(Lag1 = input$Lag1,Lag2 = input$Lag2, 
                        Lag3  = input$Lag3,Lag4 = input$Lag4,
                        Lag5  = input$Lag5))
    
    output$prediction <- renderText({predict(fit,newdata = newdata())})
  }
)


```

## How to get prediction ??

- Go to my apps [here](https://humnath5.shinyapps.io/DataProduct)
- Enter 5 enteries corresponding to Lag1,....,Lag5
- Default values for these entris is 0.1 and you can enter value between -10 to 10 in the interval of 0.25
- Press Submit button to see prediction




###**References**

- [Data Science Specialization](https://www.coursera.org/specializations/jhudatascience) Course conducted by Coursera and John Hopkins University
- [Introduction to Statistical Learning](http://www-bcf.usc.edu/~gareth/ISL/index.html)
by [Rob Tibshirani ](http://www-stat.stanford.edu/~tibs/) ,[TREVOR HASTIE](http://web.stanford.edu/~hastie/) and others

- Tutorial in [Shiny Apps](http://shiny.rstudio.com)


